Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-04-03 DGMM2025/paper.tex
adjusted visibility examples to better see line splittings
fix ?

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw[dashed] (0,0) -- (4,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
            \filldraw[black] (4,2) circle (0.05) node[anchor=north] {q1};
            \draw (0,0) -- (1,0) -- (2,0) -- (2,1) -- (3,1) -- (3,2) -- (4,2);
            \draw[dashed=gray] (-1,0) -- (-1,1) -- (0,1) -- (1,1) -- (1,2) -- (2,2) -- (2,3) -- (3,3) -- (4,3) -- (5,3) -- (5,2) -- (5,1) -- (4,1) -- (4,0) -- (3,0) -- (3,-1) -- (2,-1) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
        \end{tikzpicture}
        \hspace{\floatsep}
        \begin{tikzpicture}
            \draw[red,dashed] (0,0) -- (3,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
            \filldraw[black] (3,2) circle (0.05) node[anchor=north] {q2};
            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (2,3) -- (2,2) -- (3,2);
            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (0,4) -- (1,4) -- (2,4) -- (3,4) -- (3,3) -- (4,3) -- (4,2) -- (4,1) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
        \end{tikzpicture}
        \newline
        \newline
        \begin{tikzpicture}
            \draw[red,dashed] (0,0) -- (2,0);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
            \filldraw[black] (2,0) circle (0.05) node[anchor=north] {q3};
            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2) -- (2,1) -- (2,0);
            \draw[dashed=gray] (-1,-1) -- (-1,3) -- (3,3) -- (3,-1) -- (1,-1) -- (1,1) -- (1,-1) -- (-1,-1);
        \end{tikzpicture}
        \hspace{\floatsep}
        \begin{tikzpicture}
            \draw[red,dashed] (0,0) -- (2,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
            \filldraw[black] (2,2) circle (0.05) node[anchor=north] {q4};
            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2);
            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (1,3) -- (2,3) -- (3,3) -- (3,2) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
        \end{tikzpicture}
        \caption{Examples of visibility in 2D, only q1 is visible from p1, q2 is not visible from p2 (gets out of the star), q3 is not visible from p3 (gets out of the star from a 1-d cell), q4 is not visible from p4 (gets out of the star from a 0-d cell).}
        \label{fig:visibility-2d}
    \end{figure}

@@

            \Function{CheckI}{$I$: Interval, ComplexI: list of Interval}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in ComplexI}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cup [c-a,d-b+1]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, ComplexI: list of Interval}
                \For{each interval $I$ in VectorI}
                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{CheckI}{I, \text{ComplexI}}$
                \EndFor
                \State \Return \text{CurrentIResult}
            \EndFunction

@@

>>>>

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
            \draw[dashed] (0,0) -- (2,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
            \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
            \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
            \draw[red,dashed,thick] (0,0) -- (1.5,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
            \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
            \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
            \draw[red,dashed,thick] (0,0) -- (1,0);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
            \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
            \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
        \end{tikzpicture}
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
            \draw[red,dashed,thick] (0,0) -- (1,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
            \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
            \draw [thick] (0,0) -- (0,1) -- (1,1);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \caption{Examples of visibility in 2D, only q1 is visible from p1, q2 is not visible from p2 (gets out of the star), q3 is not visible from p3 (gets out of the star from a 1-d cell), q4 is not visible from p4 (gets out of the star from a 0-d cell).}
        \label{fig:visibility-2d}
    \end{figure}

@@

            \Function{Translation}{$I$: Interval, L: list of Interval}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in L}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cup [c-a,d-b]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, L: list of Interval}
                \For{each interval $I$ in VectorI}
                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{L}}$
                \EndFor
                \State \Return \text{CurrentIResult}
            \EndFunction

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals I and J, find $I \cup J$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection (\cup)}{\text{I, J}: list of Intervals}
                \State R \gets \emptyset
                \State k1, k2 = 0
                \While{k1 < I.nbIntervals \And k2 < J.nbIntervals}
                    \State i \gets I[k1]
                    \State j \gets J[k2]

                \EndWhile
            \EndFunction
        \end{algorithmic}
    \end{algorithm}
